\documentclass{article}
\usepackage{graphicx}
\usepackage{float}
\setlength{\parindent}{0pt}
\usepackage{caption}
\usepackage{fancyvrb}
\usepackage{tcolorbox}
\usepackage[a4paper, total={6in, 8.5in}]{geometry}
\setlength{\footskip}{80pt}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{enumitem}

\title{Project - Organizational \& Procedural Measures}
\author{Aleksander Kłap}
\date{08.06.2026}

\begin{document}

\maketitle
\pagebreak

\section{Organizational \& Procedural Measures}
\subsection{User Roles}
Three roles, enforced on PLCs, HMIs, controllers, and the robot (SR-06.2). All access uses individual accounts — no shared logins. \\

\renewcommand{\arraystretch}{1.3} % 30% more row height
\begin{tabularx}{\textwidth}{p{2.5cm} X X}
    \textbf{Role} & \textbf{Permissions} & \textbf{Typical User} \vspace{0.5em}\\
\toprule
    Operator & Monitor HMIs, access Web Interfaces. No configuration or program changes. & Student running a session \\
    \midrule
    Engineer & Upload/modify PLC programs and parameters, configure HMIs. Login through Engineering Workstation only. & Lab technician / Teacher \\
    \midrule
    Administrator &  Device configuration, user and certificate management, firewall and switch configuration. &  Lab administrator \\
    \bottomrule
\end{tabularx}
\vspace{1em}

\subsection{Backup Strategy}
Backup Strategy is specified in SR-10 (see TODO).

\begin{itemize}
    \item PLC programs, HMI configurations, and controller configs are backed up after every change.
    \item The MES database is backed up daily.
    \item Backups go to dedicated backup storage (VLAN 10) and a copy is kept offline.
    \item Recovery procedures are documented and tested at least twice per year.
\end{itemize}

\subsection{Incident Response}
\begin{itemize}
    \item Detect — Anomalies surface from the Syslog collector and firewall denied-traffic logs (SR-08). Operators report unexpected station behaviour immediately.
    \item Contain — Isolate the affected device or VLAN (disconnect or firewall block). Stop the station if process safety is in doubt.
    \item Preserve — Keep logs and alarms.
    \item Recover — Restore PLC/HMI config or MES data from the last known-good backup (SR-10.4).
    \item Document — Record what happened, the cause, and the fix. 
\end{itemize}

\end{document}

